---
title: "datafeature"
author: "Shiyu Tong"
date: "2022-11-16"
output: html_document
---




```{r}
select_data <- raw_data[raw_data$affiliation.country %in% top_countries,]
# new zealand avg rank
x = select_data$affiliation.country == 'New Zealand'
mean(which(x == TRUE))
hist(which(x == TRUE),main = "New Zealand rank distribution",xlab = 'Rank index')
# USA avg rank
x = select_data$affiliation.country == 'United States'
mean(which(x == TRUE))
hist(which(x == TRUE),main = "USA rank  distribution",xlab = 'Rank index')
# CHINA avg rank
x = select_data$affiliation.country == 'China'
mean(which(x == TRUE))
hist(which(x == TRUE),main = "CHINA rank  distribution",xlab = 'Rank index')
```


Do T test among countries

```{r}
# NZ Rank
X <- select_data$affiliation.country == 'New Zealand'
NZ_rank <- which(X == TRUE)
X <- select_data$affiliation.country == 'United States'
USA_rank <- which(X == TRUE)
X <- select_data$affiliation.country == 'China'
CH_rank <- which(X == TRUE)

```


```{r}
t.test(NZ_rank,USA_rank)
t.test(NZ_rank,CH_rank)
```

The T test result of NZ and USA. The p-value is 0.022. Smaller than 0.05. So it means that there is a difference between NZ and USA.

On the other hand. There is no difference between NZ and China.

### Check distribution




### Use all data
```{r}
filepath = 'data/raw_data/'
filelist <- list.files(filepath)
filelist
raw_data <- data.frame()
for (file in filelist){
  #cat(file)
  data <- read.csv(paste0(filepath, file))
  data$topic <- gsub('.csv','',file)
  raw_data <- rbind(raw_data,data)
}
```


```{r}
top_countries <- names(sort(table(raw_data['affiliation.country']),decreasing = TRUE)[1:30])
rank = sort(table(raw_data['affiliation.country']),decreasing = TRUE)[1:15]
plot(rank)
pie(rank, main="The Paper amount of Countries")

```

```{r}
GDP_data <- read.csv('data/GDP_data.csv')
#summary(GDP_data)
country_list <- c('United States','New Zealand','China','United Kingdom','France','India','Australia')
GDP_data = GDP_data[which(GDP_data$Country.Name %in% country_list),]
```

```{r}
# Using avg GDP 2000-2021
GDP_data = GDP_data[,colnames(GDP_data)[c(1:2,45:66)]]
GDP_data$avg_gdp <- rowMeans(GDP_data[,3:24])
GDP_data$avg_gdp <- GDP_data$avg_gdp / 10e9
```


```{r}
country_count <- table(raw_data['affiliation.country'])[country_list]
country_gdp_rate <- c()

for (country in country_list){
  country_gdp_rate <- c(country_gdp_rate,country_count[country]/GDP_data[which(GDP_data$Country.Name==country),'avg_gdp'])
}
country_gdp_rate
```

### Researcher Population
```{r}
researchers <- read.csv('data/Researchers.csv')
researchers_mean <- aggregate(researchers$Value, list(researchers$LOCATION), FUN=mean) 
country_list <- c('China','Germany','France','United Kingdom','New Zealand')
country_count <- table(raw_data['affiliation.country'])[country_list]
```


```{r}
colnames(researchers_mean) <- c('country','researchers_mean')
researchers_mean$country <- country_list
country_researcher_rate <- c()

for (country in country_list){
  country_researcher_rate <- c(country_researcher_rate,country_count[country]/researchers_mean[which(researchers_mean$country==country),'researchers_mean'])
}
round(country_researcher_rate,4)
```


### University Count
```{r}
library(dplyr)
country_list <- c('United States','New Zealand','China','United Kingdom','France','India','Australia','Germany')
university_count <- raw_data[which(raw_data$affiliation.country %in% country_list),]
university_count <- aggregate(university_count$affilname,list(university_count$affiliation.country,university_count$affilname),FUN = length )
colnames(university_count) <- c('country','university','count')
university_count <- aggregate(university_count$university,list(university_count$country),FUN = length )
colnames(university_count) <- c('country','value')
paper_count <- table(raw_data['affiliation.country'])[country_list]
```

```{r}
country_uni_rate <- c()
for (country in country_list){
  country_uni_rate <- c(country_uni_rate,paper_count[country]/university_count[which(university_count$country==country),'value'])
}
country_uni_rate
```



### average citetion count
```{r}
select_data <- raw_data[which(raw_data$affiliation.country %in% country_list),]
avg_cite <- aggregate(select_data$citedby_count,list(select_data$affiliation.country),FUN = mean)
colnames(avg_cite) <- c('country','avg_count')
avg_cite[order(avg_cite$avg_count,decreasing = TRUE),]
```

### Compare QS TOP500

```{r}
filepath = 'data/QSrank.csv'
QS500 <- read.csv(filepath,header = TRUE)
QS500 <- QS500[1:500,5:7]
# re <- c('China (Mainland)','Hong Kong SAR', 'Taiwan')
QS500[QS500$country == 'China (Mainland)','country'] <- 'China'
country_list <- c('United States','New Zealand','China','United Kingdom','France','India','Australia','Germany')
QS500 <- QS500[which(QS500$country %in% country_list),'institution']
uni_selected <- raw_data[which(raw_data$affilname %in% QS500),]
unique(uni_selected[which(uni_selected$affiliation.country == 'New Zealand'),'affilname'])
```


```{r}
uni_count <- aggregate(uni_selected$affilname,list(uni_selected$affiliation.country,uni_selected$affilname),FUN = length )
colnames(uni_count) <- c('Country','University','Count')
uni_count <- aggregate(uni_count$University,list(uni_count$Country),FUN = length)
colnames(uni_count) <- c('Country','Count')
paper_count <- table(uni_selected$affiliation.country)
country_QS500_rate <- c()
for (country in country_list){
  country_QS500_rate <- c(country_QS500_rate,paper_count[country]/uni_count[which(uni_count$Country==country),'Count'])
}
sort(country_QS500_rate,decreasing = TRUE)
```

```{r}
NZ_data <- raw_data[which(raw_data$affiliation.country =='New Zealand'),]
sort(table(NZ_data$topic),decreasing = TRUE)
```


### Compare rank unit output for each topic
```{r}
library(ggplot2)
```

```{r}
keyword <- 'geothermal'
country_list <- c('United States','New Zealand','China','United Kingdom','France','India','Australia','Germany')
temp_data <- raw_data[which(raw_data$topic == keyword & raw_data$affiliation.country %in% country_list),]
# QS 500 university count
uni_selected <- temp_data[which(temp_data$affilname %in% QS500),]
uni_count <- aggregate(uni_selected$affilname,list(uni_selected$affiliation.country,uni_selected$affilname),FUN = length )
colnames(uni_count) <- c('Country','University','Count')
uni_count <- aggregate(uni_count$University,list(uni_count$Country),FUN = length)
colnames(uni_count) <- c('Country','Count')
paper_count <- table(uni_selected$affiliation.country)
country_QS500_rate <- c()
for (country in country_list){
  country_QS500_rate <- c(country_QS500_rate,paper_count[country]/uni_count[which(uni_count$Country==country),'Count'])
}
cat('QS 500 Uni count \n')
sort(country_QS500_rate)
barplot(country_QS500_rate,las = 2,main= paste0(keyword,' QS 500 Rate'))
# Research Population
country_list <- c('China','Germany','France','United Kingdom','New Zealand')
country_count <- table(temp_data['affiliation.country'])[country_list]
colnames(researchers_mean) <- c('country','researchers_mean')
researchers_mean$country <- country_list
country_researcher_rate <- c()

for (country in country_list){
  country_researcher_rate <- c(country_researcher_rate,country_count[country]/researchers_mean[which(researchers_mean$country==country),'researchers_mean'])
}
cat('Research Population \n')
round(country_researcher_rate,4)
barplot(country_researcher_rate,las = 2,main= paste0(keyword,' Research Population Rate'))
# GDP
country_list <- c('United States','New Zealand','China','United Kingdom','France','India','Australia')
country_count <- table(temp_data['affiliation.country'])[country_list]
country_gdp_rate <- c()

for (country in country_list){
  country_gdp_rate <- c(country_gdp_rate,country_count[country]/GDP_data[which(GDP_data$Country.Name==country),'avg_gdp'])
}
cat('GDP unit output\n')
sort(country_gdp_rate)
barplot(country_gdp_rate,las = 2,main = paste0(keyword,' GDP rate'))
# avg citition count
select_data <- raw_data[which(raw_data$affiliation.country %in% country_list),]
avg_cite <- aggregate(select_data$citedby_count,list(select_data$affiliation.country),FUN = mean)
colnames(avg_cite) <- c('country','avg_count')
avg_cite[order(avg_cite$avg_count,decreasing = TRUE),]

```


```{r}
topics <- unique(raw_data$topic)
outputpath <- 'plots/'
for (keyword in topics){
    country_list <- c('United States','New Zealand','China','United Kingdom','France','India','Australia','Germany')
    temp_data <- raw_data[which(raw_data$topic == keyword & raw_data$affiliation.country %in% country_list),]
    
    
    # QS 500 university count
    uni_selected <- temp_data[which(temp_data$affilname %in% QS500),]
    uni_count <- aggregate(uni_selected$affilname,list(uni_selected$affiliation.country,uni_selected$affilname),FUN = length )
    colnames(uni_count) <- c('Country','University','Count')
    uni_count <- aggregate(uni_count$University,list(uni_count$Country),FUN = length)
    colnames(uni_count) <- c('Country','Count')
    paper_count <- table(uni_selected$affiliation.country)
    country_QS500_rate <- c()
    for (country in country_list){
      country_QS500_rate <- c(country_QS500_rate,paper_count[country]/uni_count[which(uni_count$Country==country),'Count'])
    }
    png(paste0(outputpath,keyword,' QS 500 Rate.png'))
    x <- barplot(country_QS500_rate,las = 2,main= paste0(keyword,' QS 500 Rate'))
    text(x, country_QS500_rate+0.1 , round(country_QS500_rate,2) ,cex=1)
    dev.off()
    
    # Research Population
    # country_list <- c('China','Germany','France','United Kingdom','New Zealand')
    # country_count <- table(temp_data['affiliation.country'])[country_list]
    # colnames(researchers_mean) <- c('country','researchers_mean')
    # researchers_mean$country <- country_list
    # country_researcher_rate <- c()
    # 
    # for (country in country_list){
    #   country_researcher_rate <- c(country_researcher_rate,country_count[country]/researchers_mean[which(researchers_mean$country==country),'researchers_mean'])
    # }
    # cat('Research Population \n')
    # x <- barplot(country_researcher_rate,las = 2,main= paste0(keyword,' Research Population Rate'))
    # text(x, country_researcher_rate , country_researcher_rate ,cex=1) 
    
    
    # GDP
    country_list <- c('United States','New Zealand','China','United Kingdom','France','India','Australia')
    country_count <- table(temp_data['affiliation.country'])[country_list]
    country_gdp_rate <- c()
    
    for (country in country_list){
      country_gdp_rate <- c(country_gdp_rate,country_count[country]/GDP_data[which(GDP_data$Country.Name==country),'avg_gdp'])
    }
    png(paste0(outputpath,keyword,' GDP rate.png'))
    x <- barplot(country_gdp_rate,las = 2,main = paste0(keyword,' GDP rate'))
    text(x, country_gdp_rate+0.1 , round(country_gdp_rate,2) ,cex=1) 
    dev.off()
    # avg citition count
    
  
    
    # autor rate
    autor <- aggregate(temp_data$autor,list(temp_data$affiliation.country),FUN = function(x) length(unique(x)))
    colnames(autor) <- c("Country",'Autor')
    paper_count <- table(temp_data$affiliation.country)
    autor_rate <- c()
     for (country in country_list){
        autor_rate <- c(autor_rate,paper_count[country]/autor[which(autor$Country==country),'Autor'])
     }
    png(paste0(outputpath,keyword,' Autor rate.png'))
    x <- barplot(autor_rate,las = 2,main = paste0(keyword,' Autor rate'))
    text(x, autor_rate , round(autor_rate,2) ,cex=1) 
    dev.off()
}
```

```{r}
autor <- aggregate(raw_data$autor,list(raw_data$affiliation.country),FUN = function(x) length(unique(x)))
colnames(autor) <- c("Country",'Autor')
topics <- unique(raw_data$topic)
keyword <- 'geothermal'
for (keyword in topics){
    country_list <- c('United States','New Zealand','China','United Kingdom','France','India','Australia','Germany')
    temp_data <- raw_data[which(raw_data$topic == keyword & raw_data$affiliation.country %in% country_list),]
    autor <- aggregate(temp_data$autor,list(temp_data$affiliation.country),FUN = function(x) length(unique(x)))
    colnames(autor) <- c("Country",'Autor')
    paper_count <- table(temp_data$affiliation.country)
    autor_rate <- c()
     for (country in country_list){
        autor_rate <- c(autor_rate,paper_count[country]/autor[which(autor$Country==country),'Autor'])
    }
    x <- barplot(autor_rate,las = 2,main = paste0(keyword,' Autor rate'))
    text(x, autor_rate , round(autor_rate,2) ,cex=1) 
    
    }
  

```


### Select top autor avg cititation count
```{r}
country_list <- c('United States','New Zealand','China','United Kingdom','France','India','Australia','Germany')
select_data <- raw_data[which(raw_data$affiliation.country %in% country_list),]
autor <- aggregate(select_data$citedby_count,list(select_data$autor,select_data$affiliation.country),FUN = mean)

```

index

pie chart
unit output
topic model
